Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management

### 2023-05-25 Writing/JAAEA/1stRoundRevision/reply_to_editor.rmd

---
output:
  word_document: default
  html_document: default
---
# Reply to the editor

Blur blur, . Your comments are in blue, and our responses are in black.

<span style = "color: blue;"> Based on the reviews and your email response, I have decided to give you the opportunity to revise the manuscript and respond to reviewer comments. One major point is that your true DGP assumed a quadratic plateau, but the estimated models use quadratic. This will lead the estimated models to give biased results. In your email response you indicate that you used quadratic plateau as the “true” functional form based on agronomy studies. If the dominant approach in recent literature is to use quadratic functions, then it does seem valuable to quantify the bias from using quadratic rather than quadratic plateau. Please document clearly in the manuscript that quadratic is the common practice (__point 1__). However, the title of your paper is about an economic evaluation of GWR analysis, and the choice of quadratic or quadratic-plateau is not an issue with GWR and this needs to be clear (__point 2__). Also reading through your discussion section, the implications are primarily framed about how GWR performed, but it might completely be an issue with functional form, but the current simulations don't inform us about the source of bias. Ideally, you would compare a GWR model that is quadratic with a GWR model that is quadratic-plateau functional form (__point 3__). </span>

Reply to <span style = "color: blue;"> __point 1__ </span>:

Actually, the dominant functional form used in the literature is quadratic-plateau for non-GWR (regualr parametric) regression because agronomists have long known that it better represents corn-nitrogen relationship. Application of GWR is very new to the field and GWR is not currently flexible in funcional form. There is no readily available statistical software or packages that lets researchers to use quadratic-plateau functionl form under the GWR framework. That is the primary reason that both Trevisan et al () and Rakshit et al () are using quadratic functional form. So, their choice of functional form is not coming from agronomic facts, rather from technical limitations. We are trying to point out this can be a problem with GWR just like it is a problem for regular regression framework. So, our paper is imporatnt because many use quadratic-plateau in regular regression framework, but the GWR promoted by the two studies use quadratic just because it is hard to do so. We believe it is imporatnt that this technical limitation is not trivial and would like to avoid practitioners or researcher to believe GWR is better than it truly is. We further suggest that it is important to develope a statistical package that allows to model yield-input relationship more flexibly.

Reply to <span style = "color: blue;"> __point 2__ </span>:

We fully agree with this point. We are assuming that readers know yield-nitrogen relationship is better represented by quadaratic-plateau and that point was kept implicit tghroughout the article. We made significant modifications to the manuscript so that we are not trying to blame GWR itself.

Reply to <span style = "color: blue;"> __point 3__ </span>:

This is a problem of our writing and we apologize for that. Our objective is not to evaluate the problem of GWR itself, rather the current practice of using GWR with quadratic form when the true underlying true relationship is quadratic-plateau as in Trevisan et al (). But, we agree fully that it is interesting to see how GWR performs when the assumed funtional form in regression and true functional form in the data generating process are the same. However, please note that quadratic-plateu is a non-linear model and GWR with quadratic-plate cannot be estimated readily as of now.

<span style = "color: blue;"> The other major critique of reviewer #1 is that the “true” DGP of the parameters does not correspond with a GWR. For example, reviewer #1 argues that the spatial distribution of parameters described in lines 173-193 does not correspond with a GWR DGP. Is there evidence from the agronomy literature that the DGP (aside from the functional form assumption) follows the process that you specify? Or alternatively, is there evidence from the agronomy literature that the DGP does not follow the GWR DGP described by reviewer #1 in comment #5? My guess is that the agronomy literature has little or nothing to say about this (compared to the functional form assumption), but maybe I'm wrong about that. If there is no evidence to support your proposed DGP or the GWR DGP as “true,” then it is difficult to critique GWR for not correctly estimating your proposed DGP (__specific point 1__). In your email response you state “Our choice of true yield response function is deliberate and just as valid as the data generating process Reviewer #1 recommends.” But if the DGP that you used and the DGP recommended by reviewer #1 are equally valid, then why critique GWR for not correctly estimating your DGP? To critique GWR, you need to argue that your DGP is more valid than the GWR DGP (__specific point 2__). Or you can estimate if GWR is robust to alternative, but equally valid, DGPs.

</span>

Fiest, it is important to reiterate that we are not interested in evaluating GWR itself even though our writing did give that impression, rather we are interested in evaluating GWR with quadratic functional form when the true underlying relationship is quadratic-plateau. This point alone addresses lots of your and reviwer 1's comments (as we discussed above, this is an important problem to address). We are critiqing the use of GWR with quadratic functional form when the true underlying relationship is quadratic-plateau.

Second, the data generating process suggested by reviewer is not even very different from our DGP in principle even though you seem to have an impression that they are vastly different.

While it may look complicated, the DGP suggested by the reviewer is basically the same as ours at the core (except functional form). Here is what the reviewer suggested.

$$
\begin{aligned}
y^* = X(X'W(s)X)^{-1}X'W(s)y + e^*
\end{aligned}
$$

Another way of writing this is simply

$$
\begin{aligned}
y_i = X_i\beta_i + e_i
\end{aligned}
$$

as shown in Leung, Y., Mei, C. L., & Zhang, W. X. (2000), where $\beta_i$ is the coefficient specific to observation $i$. $W(s)$ ensures that $\beta$ are spatially correlated. The choice of $W(s)$ is arbitrary and if you use the same $W(s)$ used in DGP for GWR regression as well, then you would be cheating, giving an unfair advantage to GWR because we (researchers) never know $W(s)$ in reality just like we do not know the weight matrix in spatial econometric approaches like spatial error model. This is the "correct" GWR DGP only if you know what $W(s)$ is priori.

In our DGP, we generate parameters (alpha, ... in equation )for individual $i$ in a spatially correlated manner (as opposed to what the reviewer thought). So, aside from the functional form, the only difference is in the spatial pattern of parameters. It is kind of like, we are using a different $W(s)$ in the above equation, which is an arbitrary parameter chosen by the researcher running MC simulations in the first place. In this sense, our DGP is just as "valid" as the GWR DGP.

Indeed, I would say our DGP is superior because ours is much more flexible. The DGP suggested by the reviewer cannot even accommodate non-linear model, while our DGP can use any functional relationship between $Y$ and $X$ as evident in our paper. Indeed, this is critical to our study because the data generating process <span style = "color: red;"> needs </span> to be quadratic-plateau to better represent the actual functional relationship exhibited by corn-nitogen response.

You are right that no agronomic studies suggest eigher our or the reviewer's DGP as a better DGP. However, our DGP has been used in an article in a prominent agronomy and precision agriculture journal (cite), meaning that our DGP was accepted by agronomists who reviewed them. On the other hand, the data generating process suggested by the reviewer has never been applied in the cotext of precision agriculture. Of course, we are not saying that our DGP is correct. And, this is not the main reason why we do not use the DGP suggested by the reviewer.

The reviewer clearly did not spend time trying to understand our DGP as the reviewer suggested him/herself. Also, the reviewer's criticism is based on his understanding that we are trying to test GWR itself and also test the its accuracy in parameter estimation, not EONR and profit estimation. Our impression of this reviewer from his/her comments is that he/she lacks domain knowledge and also economics.

Reply to <span style = "color: blue;"> __specific point 1__ </span>:

It seems that you have an impression that the GWR DGP is the "correct" DGP if we are estimating with GWR. But, as I argued above, there is no such thing as the "correct" DGP. In GWR DGP, the choice of $W(s)$ is arbitrary and no researchers should know it. In that sense, you are destined to misspecify the underlying DGP in a realistic situation. The most important part of the DGP is by far the functinal form of yield and nitrogen.

We will not use the GWR DGP process for two reasons. First, as we mentioned, we are not interested in criticizing GWR itself, but GWR with quadratic form when the true yield response function is better represented by quadratic-plateau (we aruged why this is important in our replies above). Also, the GWR DGP process suggested by the reviewer is limited to linear-in-parmeter model (like quadratic model). It simply cannot be used for quadratic-plateau. If we were to use quadratic functional form for our true yield-nitrogen response, then this study is completely useless and loses its significance in the literature of precision agriculture.

Reply to <span style = "color: blue;"> __specific point 2__ </span>:

First, as we have communicated in our message to you ealier, we are not interested in evaluating GWR itself. So, I do not think your comments really apply to our manuscript.

But, suppose we are interested in evaluating GWR itself. And, also suppose our DGP and the GWR DGP are very different even though they are in reality very similar as argued above. Even then, we can definitely criticize GWR by using our DGP. Nobody knows the true data generating process of OFPE in the real world. If we use the GWR DGP and find out that GWR performs well, then does that mean GWR performs well in the real world? No. It says that GWR performs well if the data generated in OFEP indeed follow GWR DGP, which of course may not be the true DGP in real world. If GWR does not perform well for a single DGP that is just as valid as GWR DGP, then that would mean we need to be careful applying GWR in the real world. This is not to say, GWR is always bad. But, it is enough to warrant researchers and practitioners that GWR <span style = "color: red;"> may </span> fail. If we show that GWR does not work well with "a" valid DGP, then it is enought to warn people about its potential danger.

<span style = "color: blue;"> In general, it is important in your paper to clarify how much of the bias you estimate is due to the functional form assumption versus the assumption about the DGP. Also, you need to more clearly defend the DGP you choose as the “true” DGP or compare results with alternative DGPs. It seems to me that you will need to rethink your simulations so that you can more clearly sort out the sources of bias. </span>

Reply:

It is not important in this paper to distinguish and isolate the sources of bias. Our interest is in showing the bias of using GWR with quadratic form (because of technical limitation) even though the underlying relatinship is quadratic-plateau (like corn-nitrogen) as done by Trevisan et al (). It is actually impossible in our paper to isolate them and we are not interested in doing so either. Also, please note that functional form is part of DGP and indeed the most important part of a DGP. There is no such thing as isolating the source of bias of funcitonal form assumption and DGP assumption.

If our interest is understanding the problem of estiamtion inaccurcy by GWR alone, then we should have used quadratic-plateau in our GWR estimation so that the functional forms match. But, this is not our interest at least in this paper and it is also technically too cumbersome at the moment because there is no readily available statistical software to implement it. We are criticizing the practice that has been used by a researcher that can have false impression about how valuable GWR is for variable rate nitrogen application in the OFEP setting.

### 2023-06-12 Writing/manuscript_gwr.rmd

#* read the results rds file
results <-
  here("Shared", "Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
  .[, bias := pi_diff_est - pi_diff] %>%
  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
  # === label price ratio
  .[, pLabelName := "Price Ratio (N/corn)"] %>%
  .[pRatio == 5.44, pLabel := "Low"] %>%
  .[pRatio == 6.56, pLabel := "Middle"] %>%
  .[pRatio == 7.67, pLabel := "High"] %>%
  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]

@@

On any given field, it is typical for U.S. Midwestern row crop farmers to pay for 1-ha grid soil sampling and chemical analysis every three or four years [@morris2018strengths]. The data is often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., Culman, et al. 2020). But the expense of soil sampling and analysis is driving development of sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics. For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx® systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages. GreenSeeker then basically uses Oklahoma State University's Sensor-based N Rate Calculator to convert those data into recommended nitrogen fertilizer (N) application rate maps ($R_xs$). Veris Technologies manufactures sensor equipment that can be towed through fields to gather apparent electroconductivity (EC) data, which can be used to infer properties of soil content. The "decision tool" software FieldRevealTM allows users to upload EC data, elevation data, and vegetative index data, which FieldRevealTM's professional agronomists analyze to provide $R_x$s to farmers. FieldApex creates N $R_x$s using foliar vegetative index data from satellite imagery, and SlantRange uses drone imagery for similar purposes.

@@

While the results reported by @trevisan2021spatial look rosy and GWR looks like a promising method, there are two potentially dangerous factors that may have caused them to snigificantly over-estimate the value of GWR as a tool to estimate site-specific EONR. First, they used quadratic functionl form in their GWR estimation even though it is widely accepted by scientific community that corn yield reseponse to nitrogen is better approximated by quadratic-plateau functional form. It is likely that their choice of quadratic functional form is merely a compromise because there did (does) not exist any statistical software of package that implements GWR with quadratic-plateau functional form. Second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application, not just @trevisan2021spatial. In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits. However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions. @trevisan2021spatial provided an example at step (3) by assuming that their GWR estimates provided "true" site-specific yield response functions. This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions. But, inaccurate estimation of yield response function in this methodology can result in significant bias in the estimation of the value of VRA. This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR.

The primary obejctive of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based variable rate application (VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form. We evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial. Both assumed a quadratic response of yield to nitrogen rate ($N$). However, while @trevisan2021spatial estimated the coefficient on $N^2$ as a global parameter, @rakshit2020 estimated it locally for each point. At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial. However, the flexibility can be a disadvantage rather than an advantage because the estimation of economically optimal nitrogen rate (EONR) is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient. It is critical to keep in mind that it is not our objective to measure the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Rather, we are interested in the economic implications of the statistical inaccuracy in estimating the coefficients of the model in this study. As part of identifying bias in the estimation of the economic value of VRA based on the GWR approaches, we evaluate their actual values. Finally, we also evaluate their relative performances compared to URA based on shape-constrained additive model approach.

@@

<span style = "color: blue;"> this needs to be rewritten </span>

@@

The spatial distributions of cell-level parameters $\alpha_{j, k}$, $\beta_{j, k}$, $\gamma_{j,k}$, $\tau_{j, k}$, and the error term $\varepsilon_{j, k}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation], and the simulation processes were conducted using the R package gstat [@graler16]. Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters. The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical). The range of 600m means that observations separated by more than 600m are spatially uncorrelated. A higher range value indicates increased spatial dependence, meaning less abrupt differences are observed between the production function parameters of neighboring cells. The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018]. Note that the range of the optimal N rates of individual rounds of simulations are narrower. In defining the magnitude of the error term, we utilized the experimental data generated through eight on-farm randomized N field trials conducted by the DIFM project in 2018 by the Data-Intensive Farm Management Project (DIFM), [@bullock2019data]. Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated. The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the value of sill variances assigned to the simulations' error terms.

@@

In each simulation, for each cell $(j, k)$, the simulation's true yield $y_{j, k}$ was generated based on the cell's assigned application rate $N_{j,k}$, true response parameters $c_{j,k} = (\alpha_{j,k}, \beta_{j,k}, \gamma_{j,k}, \tau_{j,k})$, and error term $\varepsilon\_{j,k}$. This procedure generated a field-level, cell-specific data set, $\{(y_{j, k},N_{j, k} ):j=1,\dots,1440;k=1,\dots, 6 \}$. To maintain consistency with real-world OFPEs, it was assumed that harvesting equipment could only record yields accurately at an 18m $\times$ 12m (subplot) resolution. Since every cell in a plot received the same N application rate, then so did every cell within a subplot, so $N_{j,1} = N_{j,2}= \dots = N_{j,6} = N_j$ for each subplot $j$. Letting $\mu_j$ denote the mean of the yields of the cells in subplot $j$, the analysis of each round's data was based on 1440 $(\mu_j,N_j )$ observations.

@@

Three approaches to estimate yield response functions and their associated EONRs were used. The first approach used the shape-constrained additive model (SCAM) to estimate a single yield response function for the entire field, and to estimate and economically optimal uniform nitrogen application rate for the field. The other two approaches both used GWR, but assumed different specifications in modeling the impact of nitrogen on yield. The first GWR approach (GWR-R) followed the specification used by @rakshit2020, and the second GWR approach (GWR-T) followed the specification used by @trevisan2021spatial. Further details of each approach are presented below. SCAM and GWR estimations were performed using $R$'s scam [@scam-R] and GWmodel [@gwmodel-R] packages.

@@

In the lower benchmark situation, a researcher was assumed to run OFPEs to gather data, then to estimate a single "full-field" yield response function using the SCAM non-parametric regression framework, which is a spline-based series estimation that can impose a shape-constraints on the estimated function [@pya2015shape]. In using SCAM, the yield response function was restricted to be monotonically increasing and concave with respect to the N application rate, which are traits well substantiated by agronomic research. When the chosen shape constraints are correct, SCAM is more statistically efficient than a fully non-parametric regression [@pya2015shape]. The estimated model is represented mathematically as follows,

$$y_j = \alpha + \sum_{l=1}^l \beta_l g_l(N_j)+ \varepsilon_j$$

where $g_l(\cdot)$ is the $l$th spline basis and $\beta_l$ is its coefficient to be estimated. The $\beta_l$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases as $N_j$ increases, but at a diminishing rate.

Let $\hat{f}_{scam}(\cdot)$ represent the estimated whole-yield yield response function ($\sum_{k=1}^K \hat{\beta}_k g_k(\cdot)$). Given the information derived from the SCAM approach, the estimate of the economically optimal uniform N rate is,

$$\hat{N}_{scam}^* \equiv argmax_N⁡ \big[p\cdot \hat{f}_{scam} (N)-w\cdot N\big]$$

### GWR-Rakshit (GWR-R)

The GWR-R model is simply the basic GWR model [@fotheringham1996geography; @brunsdon1999some; @fotheringham2003geographically], where subplot-specific yield responses were modeled as quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,

@@

The coefficients $\alpha_j$, $\beta_j$, and $\eta_j$ were continuous functions of subplot $j$’s coordinates ($lon_j$, $lat_j$). The GWR-R estimation produced subplot-specific estimates of coefficients $\hat{\alpha}_j$, $\hat{\beta}_j$, and $\hat{\eta}_j$, and so of the yield response function $\hat{f}_{gwr-r,j}(N)$ for $j = 1, 2, \dots, 1440$. The estimated economically optimal N application rate for subplot $j$ was calculated by solving the subplot's profit maximization problem:

$$\hat{N}_{gwr-r,j}^{*} \equiv argmax_N⁡[p\hat{f}_{gwr-r, j} (N) -wN], \;\; j \in 1, 2, \dots, 1440.$$

### GWR-Trevisan (GWR-T)

The GWR-T model is also called as “mixed” GWR in the literature [@brunsdon1999some], where some parameters are fixed globally while others vary geographically. In our model, the coefficient on $N^2$ was estimated as a global parameter while the coefficient on $N$ was estimated subplot-specifically. For each subplot $j \in {1, 2, \dots, 1440}$, the assumed yield response was,

@@

Let $\hat{f}_{gwr-t,j}(N)$ for $j = 1, 2, \dots, 1440$ denote the estimated yield response function for subplot $j$. The estimated economically optimal N application rate for subplot $j$ was then,

$$\hat{N}^*_{gwr-t,j} \equiv argmax_N⁡[p\hat{f}_{gwr-t,j} (N) -wN] .$$

The Gaussian kernel function was used when estimating both GWR models, and the optimal bandwidth was selected through the corrected AIC approach [@fotheringham2003geographically]. The optimal bandwidth differed slightly across each simulated experiment, and the average bandwidth was around 18 meters.

## The value of GWR-based VRA over scam-based URA

@@

$$\Pi_{scam}^* = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, k} (\hat{N}_{scam}^* )-w\hat{N}_{scam}^*\big]$$

@@

For $m = R, T$, the true per-ha net revenues ("profits") resulting from applying the profit-maximizing cell-specific N rate plan estimated by GWR-m were,

$$\Pi_{gwr-m}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, k} (\hat{N}_{gwr-m, j}^*)-w\hat{N}_{gwr-m,j}^*]$$

where $f_{j, k} (\hat{N}_{gwr-j}^*)$ denote the true yield generated at cell $(j, k)$ with subplot $l$'s N rate.

@@

$$\Delta_{gwr-m} = \Pi_{gwr-m} - \Pi_{scam} .$$

@@

$$\hat{\Delta}_{gwr-m} = \hat{\Pi}_{gwr-m}^* - \hat{\Pi}_{scam}^*$$

>>>>

#* read the results rds file
results <-
  here("Shared", "Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
  .[, bias := pi_diff_est - pi_diff] %>%
  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
  # === label price ratio
  .[, pLabelName := "Price Ratio (N/corn)"] %>%
  .[pRatio == 5.44, pLabel := "Low"] %>%
  .[pRatio == 6.56, pLabel := "Middle"] %>%
  .[pRatio == 7.67, pLabel := "High"] %>%
  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]

@@

On any given field, it is typical for U.S. Midwestern row crop farmers to pay for 1-ha grid soil sampling and chemical analysis every three or four years [@morris2018strengths]. The data are often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., Culman, et al. 2020). But the expense of soil sampling and analysis is driving development of sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended nitrogen fertilizer (N) application rate maps (usually called "prescriptions" or $R_x$s).^[For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx® systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages. GreenSeeker then uses Oklahoma State University's Sensor-based N Rate Calculator to convert those data into recommended nitrogen fertilizer (N) $R_x$s. Veris Technologies manufactures sensor equipment that can be towed through fields to gather apparent electroconductivity (EC) data, which can be used to infer properties of soil content. The "decision tool" software FieldRevealTM allows users to upload EC data, elevation data, and vegetative index data, which FieldRevealTM's professional agronomists analyze to provide $R_x$s to farmers. FieldApex creates N $R_x$s using foliar vegetative index data from satellite imagery, and SlantRange uses drone imagery for similar purposes.]

@@

While the results reported by @trevisan2021spatial look rosy and GWR looks like a promising method, there are two potentially dangerous factors that may have caused them to significantly over-estimate the value of GWR as a tool to estimate site-specific EONR. First, they used quadratic functional form in their GWR estimation even though it is widely accepted by scientific community that corn yield response to nitrogen is better approximated by quadratic-plateau functional form. It is likely that their choice of quadratic functional form is merely a compromise because there did (does) not exist any statistical software of package that implements GWR with quadratic-plateau functional form.

The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application, not just @trevisan2021spatial. In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits. However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions. @trevisan2021spatial provided an example at step (3) by assuming that their GWR estimates provided "true" site-specific yield response functions. This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions. But, inaccurate estimation of yield response function in this methodology can result in significant bias in the estimation of the value of VRA. This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR.

The primary objective of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based variable rate application (VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form. We evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial. Both of them assumed a quadratic response of yield to nitrogen rate ($N$). However, while @trevisan2021spatial estimated the coefficient on $N^2$ as a global parameter, @rakshit2020 estimated it locally for each point. At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial. However, the flexibility can be a disadvantage rather than an advantage because the estimation of economically optimal nitrogen rate (EONR) is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient. It is critical to keep in mind that it is not our objective to measure the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Rather, we are interested in the economic implications of the statistical inaccuracy in estimating the coefficients of the model in this study. As part of identifying bias in the estimation of the economic value of VRA based on the GWR approaches, we evaluate their actual values. Finally, we also evaluate their relative performances compared to URA based on shape-constrained additive model approach.

@@

@@

The spatial distributions of cell-level parameters $\alpha_{j, k}$, $\beta_{j, k}$, $\gamma_{j,k}$, $\tau_{j, k}$, and the error term $\varepsilon_{j, k}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation], and the simulation processes were conducted using the R package gstat [@graler16]. Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters. The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical). The range of 600m means that observations separated by more than 600m are spatially uncorrelated. A higher range value indicates increased spatial dependence, meaning less abrupt differences are observed between the production function parameters of neighboring cells. The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018]. Note that the range of the optimal N rates of individual rounds of simulations are narrower. In defining the magnitude of the error term, we utilized the experimental data generated through eight on-farm randomized N field trials conducted by the Data-Intensive Farm Management Project (DIFM) project in 2018 [@bullock2019data]. Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated. The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the square root value of the sill variances assigned to the simulations' error terms.

@@

In each simulation, for each cell $(j, k)$, the simulation's true yield $y_{j, k}$ was generated based on the cell's assigned application rate $N_{j,k}$, true response parameters $c_{j,k} = (\alpha_{j,k}, \beta_{j,k}, \gamma_{j,k}, \tau_{j,k})$, and error term $\varepsilon_{j,k}$. This procedure generated a field-level, cell-specific data set, $\{(y_{j, k},N_{j, k} ):j=1,\dots,1440;k=1,\dots, 6 \}$. To maintain consistency with real-world OFPEs, it was assumed that harvesting equipment could only record yields accurately at an 18m $\times$ 12m (subplot) resolution. Since every cell in a plot received the same N application rate, then so did every cell within a subplot, so $N_{j,1} = N_{j,2}= \dots = N_{j,6} = N_j$ for each subplot $j$. Letting $\mu_j$ denote the mean of the yields of the cells in subplot $j$, the analysis of each round's data was based on 1440 $(\mu_j,N_j )$ observations.

@@

Three approaches to estimate yield response functions and their associated EONRs were used. The first approach used the shape-constrained additive model (SCAM) to estimate a single yield response function for the entire field, and to estimate an economically optimal uniform nitrogen application rate for the field. The other two approaches both used GWR, but assumed different specifications in modeling the impact of nitrogen on yield. The first GWR approach (GWRR) followed the specification used by @rakshit2020, and the second GWR approach (GWRT) followed the specification used by @trevisan2021spatial. Further details of each approach are presented below. SCAM and GWR estimations were performed using $R$'s scam [@scam-R] and GWmodel [@gwmodel-R] packages.

@@

In the lower benchmark situation, a researcher was assumed to run OFPEs to gather data and then to estimate a "full-field" uniform yield response function using the SCAM non-parametric regression framework [@pya2015shape]. SCAM is a type of generalized additive model (GAM) [@hastie1986gam] which allows for more flexible and non-linear  relationships between the response variable and the predictors through a combination of smooth functions (also known as "splines"). In comparison with the conventional GAM technique, SCAM allows for the imposing of shape constraints on the estimated relationship, which is particularly useful when prior knowledge or theoretical considerations suggest certain shape restrictions of the relationship. In the SCAM of this study, the yield response function was restricted to be monotonically increasing and concave with respect to the N application rate, which are traits well substantiated by agronomic research [@cerrato1990comparison; @bullock1994quadratic]. When the chosen shape constraints are correct, SCAM is more statistically efficient than a fully non-parametric regression [@pya2015shape]. The estimated model is represented mathematically as follows,

$$y_j = \alpha + \sum_{k=1}^K \beta_k g_k(N_j)+ \varepsilon_j$$

where $g_k(\cdot)$ is the $k$th spline basis and $\beta_k$ is its coefficient to be estimated. The $\beta_k$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases as $N_j$ increases, but at a diminishing rate.

Let $\hat{f}^{SCAM}(\cdot)$ represent the estimated whole-yield yield response function ($\sum_{k=1}^K \hat{\beta}_k g_k(\cdot)$). Given the information derived from the SCAM approach, the estimate of the economically optimal uniform N rate is,

$$\hat{N}^{*SCAM} \equiv argmax_N⁡ \big[p\cdot \hat{f}^{SCAM} (N)-w\cdot N\big]$$

### GWR-Rakshit (GWRR)

The GWRR model is simply the basic GWR model [@fotheringham1996geography; @brunsdon1999some; @fotheringham2003geographically], where subplot-specific yield responses were modeled as quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,

@@

The coefficients $\alpha_j$, $\beta_j$, and $\eta_j$ were continuous functions of subplot $j$’s coordinates ($lon_j$, $lat_j$). The GWRR estimation produced subplot-specific estimates of coefficients $\hat{\alpha}_j$, $\hat{\beta}_j$, and $\hat{\eta}_j$, and so of the yield response function $\hat{f}^{GWRR}_j(N)$ for $j = 1, 2, \dots, 1440$. The estimated economically optimal N application rate for subplot $j$ was calculated by solving the subplot's profit maximization problem:

$$\hat{N}^{*GWRR}_j \equiv argmax_N⁡[p\hat{f}^{GWRR}_j (N) -wN], \;\; j \in 1, 2, \dots, 1440.$$

### GWR-Trevisan (GWRT)

The GWRT model is also called as “mixed” GWR in the literature [@brunsdon1999some], where some parameters are fixed globally while others vary geographically. In our model, the coefficient on $N^2$ was estimated as a global parameter while the coefficient on $N$ was estimated subplot-specifically. For each subplot $j \in {1, 2, \dots, 1440}$, the assumed yield response was,

@@

Let $\hat{f}^{GWRT}_j(N)$ for $j = 1, 2, \dots, 1440$ denote the estimated yield response function for subplot $j$. The estimated economically optimal N application rate for subplot $j$ was then,

$$\hat{N}^{*GWRT}_j \equiv argmax_N⁡[p\hat{f}^{GWRT}_j (N) -wN] .$$

The Gaussian kernel function was used when estimating both GWR models (other kernel functions were also tried and the final conclusions are quantitatively similar; see appendix). For the optimal kernel bandwidth selection, while there are several frequently used approaches in the literature such as cross-validation [@cleveland1979robust; @bowman1984alternative] and Akaike Information Criterion (AIC) [@akaike1973], this study used the corrected version of the AIC approach following the most recent GWR literature [@fotheringham2003geographically; @fotheringham2017multiscale; @lu2017geographically], which is also the same approach used by @rakshit2020 and @trevisan2021spatial. The optimal bandwidth differed slightly across each simulated experiment, and the average bandwidth was around 18 meters.

## The value of GWR-based VRA over SCAM-based URA

@@

$$\Pi^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, k} (\hat{N}^{*SCAM})-w\hat{N}^{*SCAM}\big]$$

@@

The true per-ha net revenues ("profits") resulting from applying the profit-maximizing cell-specific N rate plan estimated by GWR (either GWRR or GWRT) model were,

$$\Pi^{GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, k} (\hat{N}^{*GWR}_j)-w\hat{N}^{*GWR}_j]$$

where $f_{j, k} (\hat{N}^{*GWR}_j)$ denote the true yield generated at cell $(j, k)$ with subplot $j$'s GWR estimated N rate.

@@

$$\Delta^{GWR} = \Pi^{GWR} - \Pi^{SCAM} .$$

@@

$$\hat{\Delta}^{GWR} = \hat{\Pi}^{*GWR} - \hat{\Pi}^{*SCAM}$$
